Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (6)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We thank the reviewer for this comment. We did as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools. The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis, as described in Section 4 of the paper), so it seems that this comparison is not adequate}.

Note that model checking and software simulations are two different techniques that use mathematical models. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in \textcolor{red}{Section 1 (Introduction).}
\end{resposta}

>>>>

\begin{resposta} 
We thank the reviewer for this comment. We implemented as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools. The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.

Note that model checking and software simulations are two different techniques that use mathematical models. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in Section 1 (Introduction).
\end{resposta}
